Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-11-27 tesis_hiram/Chapter3/chapter3.tex
fixes

The analysis described in this chapter is a summary of the publication from the CMS collaboration using 35.9 fb$^{-1}$ of Run II data~\cite{th1}. Monte Carlo simulations and event yields shown below and used in the analysis described in the next chapter are obtained from this publication.

>>>>

The analysis described in this chapter is a summary of the publication from the CMS collaboration using 35.9 fb$^{-1}$ of Run II data~\cite{th1}.
%Monte Carlo simulations and event yields shown below and used in the analysis described in the next chapter are obtained from this publication.
Monte Carlo simulations and event yields shown below, and used in the statistical analysis described in the next chapter, are obtained from this publication.
